Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-30 paper.qmd
Changed the Figure 8 (b) with bin counts

cell_count_scurve <- ggplot(df_bin_centroids_all, 
                            aes(x = reorder(as.factor(hexID), 
                                            -std_counts), 
                                y = std_counts,
                                group = a1,
                                color = a1)) + 
  geom_line() + 
  geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  scale_colour_continuous_sequential(palette = "Magenta") +
  xlab("hexagon id (re-ordered)") + 
  ylab("standardized bin count") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12))
```

>>>>

cell_count_scurve <- ggplot(df_bin_centroids_all, 
                            aes(x = reorder(as.factor(hexID), 
                                            -bin_counts), 
                                y = bin_counts,
                                group = a1,
                                color = a1)) + 
  geom_line() + 
  # geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  scale_colour_continuous_sequential(palette = "Magenta") +
  xlab("hexagon id (re-ordered)") + 
  ylab("standardized bin count") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12))
```
